Counterexamples in Mathematical Relations

### 2024-10-10 Relations/CounterExamples.tex
counterexamples

>>>>

\subsection{ARS in Agda}
Important counterexamples:
\begin{enumerate}
  \item $a,b,c,d$ with sinks $a$ and $d$ and a 2-cycle between $b$ and $c$.
  Counterexample to:
  \begin{itemize}
      \item WCR and WN implies CR.
  \end{itemize}
  \item Loop $a \to a$.
  Counterexample to:
  \begin{itemize}
    \item $\omega$-bounded and RP implies SN
    \item $\omega$-bounded and RP implies WN
  \end{itemize}
  \item Infinite sequence $a_0 \to a_1 \to \cdots$. Falsifies:
  \begin{itemize}
    \item $WN$
    \item $\omega$-bounded
    \item $WCR \to WN$
    \item $CR \to WN$
    \item $CR, CP \to WN$
    \item $CR, CP \to \omega$-bounded
  \end{itemize}
  \item Infinite sequence $a_0 \to a_1 \to \cdots$ with a colimit $a_\infty$,
  with each $a_n \to a_\infty$ and $a_\infty$ a normal form.
  \item Infinite sequence $a_0 \to a_1 \to \cdots$, together with links
  $a_n \to a_0$, for each $n$.
  \item The combination of the last two.
  Counterexample to
  \begin{itemize}
    \item RP
  \end{itemize}
  \item An ``infinite haircomb''. Infinite sequence $a_0 \to a_1 \to \cdots$, together with
  a disjoint, discrete set $b_0, b_1, \dots$, and links $a_n \to b_n$.
  Counterexample to:
  \begin{itemize}
    \item $WN\to WCR$
    \item $WN \to SN$
  \end{itemize}
  \item A variation of the above with backlinks $a_n \to a_0$ for all $n$.
\end{enumerate}
